Evolutionary algorithms in a volunteer computing system: performance assessment

### 2016-03-11 PPSN2016/paper.Rnw
Filtering now by number of PUTs
This is a rather lame heuristic and I'm sure it can be beat, but it shows that if you take that "dummies" out experiments take much longer and need many more inputs.

@@

>>>>

experiment.aggregates.filtered <- data.frame(Experiment=character(),
                                             milliseconds=character(),
                                             IPs=character(),
                                             actualIPs = character(),
                                             PUTss = character(),
                                             actualPUTs = character());

@@

    this.data <- this.data[this.data$actualPUTs>=10,]
    experiment.aggregates.filtered <- rbind( experiment.aggregates.filtered,
                                            data.frame( Experiment=i,                   
                                                       milliseconds=median(as.integer(this.data$milliseconds)),
                                                       IPs=median(as.integer(this.data$IPs)),
                                                       actualIPs=median(as.integer(this.data$actualIPs)),
                                                       PUTs=median(as.integer(this.data$PUTs)),
                                                       actualPUTs=median(as.integer(this.data$actualPUTs))))
